Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-07-28 ms.tex
updated the BOSZ comparison to use a convolved stellar spectrum.
Added a better spectrum which is the median combination of all frames. Also tweaked the convolution kernel slightly to better match the data.

\subsection{Comparison to BOSZ}
The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it can be compared to the measurements without convolving the Subaru spectra.
We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.

@@

>>>>

\subsection{Comparison to BOSZ}
The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it can be compared to the measurements without convolving the Subaru spectra.
We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
The models are convolved with a Gaussian that has a standard deviation $\sigma_G = 1/57700$  to obtain a resolution of 50,000.

@@

We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
Also, we average ll available spectra from the Masuda reduction to increate the signal to noise.
The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
Interestingly, the median spectrum has weaker features than the individual spectrum, perhaps because it is variable but also it could be part of the median process.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZMedian}
\end{centering}
\end{figure}
